---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CharVar

<!-- badges: start -->
<!-- badges: end -->

The goal of CharVar is to characterize 3'UTR variants into their potential regulatory elements.

## Installation

You can install the development version of CharVar like so:

First, make sure you have miniconda, pip, and bedtools installed locally (https://docs.conda.io/en/latest/miniconda.html, https://pip.pypa.io/en/stable/installation/, https://bedtools.readthedocs.io/en/latest/content/installation.html). You can then install the development version of CharVar like so:

``` r
#first, install R package: 
devtools::install_github("RomoL2/CharVar") #note, does not install large files
```

Then, in the CharVar directory in command line install the necessary annotation files, like so (if you are not sure where this directory is, try .libPaths() in R):
``` r
cd /Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar
mkdir tmp
git clone https://github.com/RomoL2/CharVar ./tmp #clones repository into temporary directory
rm -r extdata #remove directory with symbolic links
mv tmp/inst/extdata ./ #replace with directory with real annotation files
rm -r tmp #ok to override, type "y" #remove temporary directory
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CharVar)
install_reqs('/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar')
CharacterizeVariants('file.vcf', '~/', '/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar', '~/')
CharacterizeVariants_single_input("/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar", "~/")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
