---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CharVar

<!-- badges: start -->
<!-- badges: end -->

The goal of CharVar is to characterize 3'UTR variants into their potential regulatory elements.

## Installation

You can install the development version of CharVar like so:

``` r
#first, install R package: 
devtools::install_github("RomoL2/CharVar") #note, does not install large files

#Then, in the CharVar directory in command line install the necessary files, for example:
pip install github-clone #installs the package to clone subdirectories
cd /Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar
rm -r extdata #removes the sym link files from github
ghclone https://github.com/RomoL2/CharVar/tree/main/inst/extdata #downloads the real gz zipped files to the correct directory
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CharVar)
library(CharVar)
install_reqs('/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar')
CharacterizeVariants('file.vcf', '~/', '/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar', '~/')
CharacterizeVariants_single_input("/Library/Frameworks/R.framework/Versions/4.0/Resources/library/CharVar", "~/")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
